---
title: "recovery_obs_final"
output: html_document
date: '2022-09-03'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}


library(tidyverse)
library(hexbin)
library(patchwork)
library(RSQLite)
library(here)
library(janitor)
library(lubridate)

library(hrbrthemes)
library(viridis)
library(ggplot2)
library(reshape2)
```

created a data frame containg the excel csv sheet
```{r}
recovery_observations <- read_csv(here("data","Recovery_Observations.csv")) %>%
  clean_names()

```

Changed temperature column to a factor and removed all na values
```{r}
recovery_observations_t <- recovery_observations %>% 
  select(date, temperature_treatment,duration, genet, number_open_complete,number_semi_open, number_closed) %>% 
  filter(!is.na(number_open_complete)) %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp_c= as.factor(temperature_treatment))

```

Graphed with out genets and only the date, temp duration + avg open, avg semi and avg close
```{r}
grouped <- recovery_observations_t %>% 
  mutate(not_open= (number_semi_open + number_closed)) %>% 
  group_by(date, temp_c,duration) %>%
  summarize(avg_open = mean(number_open_complete),
          avg_close = mean(not_open)) %>% 
  mutate(duration= factor(duration,levels = c("24hr", "3days", "1week")))

ggplot(grouped, aes(x=temp_c, y= avg_open))+ 
  geom_boxplot()+
  facet_wrap(facets = vars(duration))+
  geom_jitter(color="black", size= 0.4, alpha= 7, width = 0.01)+
  labs(title = "Open c. Californica polyps per temperature & duration", x= "Temperature in 째C", y= "Average Open")+
  theme_bw()

ggsave(here("figures","Open c. Californica polyps per temperature & duration.png"),
       width= 10, height= 7)
```

Checking the significant values for the number of polyps that wer opened
```{r}
group_24 <- grouped %>% 
  filter(duration=="24hr")
cory_anova <-aov(data=group_24,avg_open~temp_c) 
summary(cory_anova)
TukeyHSD(cory_anova)

group_3days <- grouped %>% 
  filter(duration=="3days")
cory_anova <-aov(data=group_3days,avg_open~temp_c)
summary(cory_anova)
TukeyHSD(cory_anova)

group_week <- grouped %>% 
  filter(duration=="1week")
cory_anova <-aov(data=group_week,avg_open~temp_c)
summary(cory_anova)
TukeyHSD(cory_anova)
```


observing the graphed with out genets and only the dat, temp duration + avg close
```{r}

ggplot(group_week, aes(x=temp_c, y= avg_close))+ 
  geom_boxplot()+
  #facet_wrap(facets = vars(duration))+
  geom_jitter(color="black", size= 0.4, alpha= 7,width = 0.01)+
  labs(title = "Closed c. Californica polpys per temperature during a marine heatwave simulation", x= "Temperature in 째C", y= "Average Closed")+
  theme_bw()

ggsave(here("figures","Closed c. Californica polpys per temperature during a marine heatwave simulation.png"),
       width= 10, height= 7)
  
```

```{r}

group_24_c <- grouped %>% 
  filter(duration=="24hr")

cory_anova <-aov(data=group_24_c,avg_close~temp_c) 
summary(cory_anova)
TukeyHSD(cory_anova)


group_3days_c <- grouped %>% 
  filter(duration=="3days")

cory_anova <-aov(data=group_3days_c,avg_close~temp_c) 
summary(cory_anova)
TukeyHSD(cory_anova)

group_week_c <- grouped %>% 
  filter(duration=="1week")

cory_anova <-aov(data=group_week_c,avg_close~temp_c) 
summary(cory_anova)
TukeyHSD(cory_anova)

```

```{r}
recovery_observations_t_d <- recovery_observations %>% 
  select(date, temperature_treatment,duration, genet,total_polyps, number_open_complete,number_semi_open, number_closed) %>% 
  filter(!is.na(number_open_complete)) %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp_c= as.factor(temperature_treatment))

grouped_death <- recovery_observations_t_d %>% 
  mutate(not_open= (number_semi_open + number_closed)) %>% 
  group_by(date, temp_c,duration, total_polyps, genet) %>%
  #summarize(avg_open = mean(number_open_complete),
         # avg_close = mean(not_open)) %>% 
  mutate(duration= factor(duration,levels = c("24hr", "3days", "1week")))

ggplot(grouped_death, aes(x=date, y=total_polyps, group=genet))+
  geom_line(aes(color=genet))+
  facet_wrap(facets = vars(duration))+
  scale_color_manual(values = c("1"="#FF5733","2"="#CD2E05","3"="#BA7F6D"))+
  labs(title = "Total c. Californica polpys vs death rates", x= "Day", y= "Total Polyps")+
  theme_bw()
```

imported death rates data set
```{r}
death_obs <- read_csv(here("data","death_obs.csv")) %>%
  clean_names() %>% 
  mutate(date= mdy(date))
```

I dont know what i was doing here
```{r}
death_obs_genet <- death_obs%>% 
  select(date, temperature_treatment_c, genet,original, current_n,duration) %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temperature_c= as.factor(temperature_treatment_c))
 
death_obs_genet_ex <- death_obs_genet[-649:-792 ,] %>% 
  group_by(date, genet,duration) %>% 
  summarize(original= mean(original),
            current_n= mean(current_n))
death_obs_genet_ex <- death_obs_genet[-649:-792 ,] %>% 
  group_by(date, genet,duration) %>% 
  summarise(original= sum(original),
            current_n= sum(current_n)) %>%
  filter(genet=="3", 
         duration == "1week")

death_1 <- death_obs %>%
  filter(genet=="3", 
         duration == "1week")

ggplot(death_obs_genet_ex, aes(x=date, y=current_n, color=genet))+
  geom_line()+
  facet_wrap(facets = vars(duration))

```


```{r}
recovery_merge <- recovery_observations %>% 
  #filter(!is.na(number_open_complete)) %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp_c= as.factor(temperature_treatment)) %>% 
  mutate(date= mdy(date)) %>% 
  mutate(temp=gsub("째C","",temp_c)) %>% 
  select(date,  time, temp, duration ,genet ,total_polyps , number_open_complete,
         number_semi_open, number_closed) %>% 
  distinct() %>% 
  #mutate_all(number_open_complete, replace_na(0)) %>% 
  replace(is.na(.), 0)# %>% 
  #select(date, time, temp, duration ,genet ,total_polyps)
  
  
str(recovery_merge)
death_merge <- death_obs %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp= as.factor(temperature_treatment_c)) %>% 
  mutate(date= ymd(date)) %>% 
  select(date, day_2, time, temp, duration, genet,original, current_n,actual_day )%>% 
  distinct()
```

```{r}
#death_merge <- death_obs %>% 
  #mutate(genet=as.character(genet)) %>% 
  #mutate(temp= as.factor(temperature_treatment_c)) %>% 
  #mutate(date= ymd(date)) %>% 
  #select(date, time, temp, duration, genet, original, current_n,actual_day )%>% 
  #distinct()
```
```{r}
death_recovery <- full_join(recovery_merge,death_merge) %>% 
  distinct()

str(death_merge)
```

Generated the Death rate Figure
```{r}
death <- death_recovery %>% 
  #mutate(day=as.factor(actual_day)) %>% 
  mutate(day=as.factor(day_2)) %>% 
   #mutate(actual= current_n/original) %>% 
  group_by(day, genet,duration, total_polyps) %>% 
  summarise(original= sum(original), 
           current_n=sum(current_n)) %>% 
  filter(day!= "0") %>% 
   mutate(duration= factor(duration,levels = c("24hr", "3days", "1week"))) %>% 
  distinct()
  
  death_dup <- death %>% 
  duplicated()
  #%>% 
  #filter(!is.na(current_n)) %>% 
  #filter(!is.na(original))
  

ggplot(death, aes(x=day, y=current_n, group=genet))+
  geom_line(aes(color=genet))+
  facet_wrap(facets = vars(duration))+
  scale_color_manual(values = c("1"="#FF5733","2"="#CD2E05","3"="#BA7F6D"))+
  labs(title = "Total c. Californica polpys vs death rates", x= "Day", y= "Total Polyps")+
  theme_bw()

#ggsave(here("figures","Total c. Californica polpys vs death rates.png"),
       #width= 10, height= 7)
```
Why not just graph the death observations by themselves
```{r}
death_obs_2 <- death_obs %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp= as.factor(temperature_treatment_c)) %>% 
  mutate(date= ymd(date)) %>% 
  select(date, time, temp, duration, genet, current_n,actual_day )%>%
  #filter(duration== "1week") %>% 
   mutate(day=as.factor(actual_day)) %>% 
  group_by(day, genet,duration) %>% 
  summarise(#original= sum(original), 
           current_n= sum(current_n)) %>% 
  mutate(duration= factor(duration,levels = c("24hr", "3days", "1week")))


death_2 <- death_recovery %>% 
  mutate(day=as.factor(actual_day)) %>% 
  group_by(day, genet,duration) %>% 
  summarise(original= sum(original), 
           current_n= sum(current_n)) %>% 
  mutate(duration= factor(duration,levels = c("24hr", "3days", "1week")) #%>% 
  filter(duration== "1week")) #%>% 
  #filter(!is.na(current_n)) %>% 
  #filter(!is.na(original))

ggplot(death_obs_2, aes(x=day, y=current_n, group=genet))+
  geom_line(aes(color=genet))+
  facet_wrap(facets = vars(duration))+
  scale_color_manual(values = c("1"="#FF5733","2"="#CD2E05","3"="#BA7F6D"))+
  labs(title = "Total c. Californica polpys vs death rates", x= "Day", y= "Total Polyps")+
  theme_bw()

```

Looking at the recovery merge data
```{r}
recovery_death <- recovery_observations %>% 
  #filter(!is.na(number_open_complete)) %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp_c= as.factor(temperature_treatment)) %>% 
  mutate(date= mdy(date)) %>% 
  mutate(temp=gsub("째C","",temp_c)) %>% 
  select(date, time, temp, duration ,genet ,total_polyps , number_open_complete,
         number_semi_open, number_closed) %>% 
  distinct() %>% 
  #mutate_all(number_open_complete, replace_na(0)) %>% 
  replace(is.na(.), 0) %>%
  mutate(duration= factor(duration,levels = c("24hr", "3days", "1week"))))
  #select(date, time, temp, duration ,genet ,total_polyps)

ggplot(recovery_death, aes(x=date, y=total_polyps, group=genet))+
  geom_point(aes(color=genet))+
  facet_wrap(facets = vars(duration))+
  scale_color_manual(values = c("1"="#FF5733","2"="#CD2E05","3"="#BA7F6D"))+
  labs(title = "Total c. Californica polpys vs death rates", x= "Day", y= "Total Polyps")+
  theme_bw()
```

```{r}
ggplot(death, aes(x=day, y=current_n, group=genet))+
  geom_line(aes(color=genet))+
  facet_wrap(facets = vars(duration))+
  scale_color_manual(values = c("1"="#ED1904","2"="#FFA13E","3"="#7A450E"))+
  labs(title = "Total c. Californica polpys vs death rates", x= "Day", y= "Total Polyps")+
  theme_bw()

ggsave(here("figures","Total c. Californica polpys vs death rates.png"),
       width= 10, height= 7)
```


```{r}
death_24 <- death %>% 
  filter(duration=="24hr")

cory_anova_24 <-aov(data = death_24,current_n  ~ day) 
summary(cory_anova_24)
TukeyHSD(cory_anova_24)

death_3days <- death %>% 
  filter(duration=="3days")

cory_anova_3days <-aov(data=death_3days,current_n~day)
summary(cory_anova_3days)
TukeyHSD(cory_anova_3days)

death_week <- death %>% 
  filter(duration=="1week")

cory_anova_week <-aov(data=death_week,current_n~day)
summary(cory_anova_week)
TukeyHSD(cory_anova_week)
```


```{r}
ggplot(death, aes(x=day, y=current_n, group=duration))+
  geom_line(aes(color=duration))+
  facet_wrap(facets = vars(genet))+
  #scale_color_manual(values = c("1"="#FF5733","2"="#CD2E05","3"="#BA7F6D"))+
  labs(title = "Total c. Californica polpys vs death rates", x= "Day", y= "Total Polyps")+
  theme_bw()

```

