---
title: "Recovery_Obs"
output: html_document
date: '2022-07-30'
---
Installed packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)


```


```{r}


library(tidyverse)
library(hexbin)
library(patchwork)
library(RSQLite)
library(here)
library(janitor)
library(lubridate)

library(hrbrthemes)
library(viridis)
library(ggplot2)
library(reshape2)
```

created a data frame containg the excel csv sheet
```{r}
recovery_observations <- read_csv(here("data","Recovery_Observations.csv")) %>%
  clean_names()

```
selecting only the 24hr duration data and filtered "na" 
```{r}
day_duration <- recovery_observations %>% 
  select(date, temperature_treatment,duration, genet, number_open_complete,number_semi_open, number_closed) %>% 
  filter(duration %in% ("24hr")) %>% 
  select(date, temperature_treatment,duration, genet, number_open_complete,number_semi_open, number_closed) %>% 
  filter(!is.na(number_open_complete)) %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp_c= as.factor(temperature_treatment))
```

made another data set with everything
```{r}
recovery_observations_t <- recovery_observations %>% 
  select(date, temperature_treatment,duration, genet, number_open_complete,number_semi_open, number_closed) %>% 
  filter(!is.na(number_open_complete)) %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp_c= as.factor(temperature_treatment))

```


average opened in box plot, grouped by genets and colored by temp.
separated by duration
```{r}
duration_avg_all <- recovery_observations_t %>%
  mutate(not_open= (number_semi_open+ number_closed)) %>% 
  group_by(date, temp_c,duration, genet) %>%
  summarize(avg_open = mean(number_open_complete),
          avg_close = mean(not_open))



one <- recovery_observations_t %>% 
  group_by(date, temp_c,duration) %>%
  summarize(avg_open = sum(number_open_complete),
            avg_semi = mean(number_semi_open), avg_close = mean(number_closed))


ggplot(duration_avg_all, aes(x=genet, y= avg_open))+ 
  geom_boxplot(aes(fill= temp_c))+
  facet_wrap(facets = vars(duration))+
  geom_jitter(color="black", size= 0.4, alpha= 0.9)+
  theme_bw()

```
average closed in box plot, grouped by genets and colored by temp.
separated by duration
```{r}

ggplot(duration_avg_all, aes(x=genet, y= avg_close))+ 
  geom_boxplot(aes(fill= temp_c))+
  facet_wrap(facets = vars(duration))+
  theme_bw()

```

Average semi open in box plot, grouped by genets and colored by temp.
separated by duration
```{r}
ggplot(duration_avg_all, aes(x=genet, y= avg_semi))+ 
  geom_boxplot(aes(fill= temp_c))+
  facet_wrap(facets = vars(duration))+
  geom_jitter(color="black", size= 0.4, alpha= 0.3,width = 0.05)+
  theme_bw()


```
Figuring out barplots by creating two separate duration treatment data frames
```{r}
duration_long <- duration_avg_all %>% 
  pivot_longer(names_to = "status", values_to = "n", cols = 5:7)

ggplot(duration_long, aes(x=genet,y=n, fill= status)) + 
  geom_bar(position="fill", stat="identity")+
  facet_wrap(facets = vars(duration))+
  theme_bw()

duration_long_day <- duration_long %>% 
  filter(duration== "24hr")

ggplot(duration_long_day, aes(x=genet,y=n, fill= status)) + 
  geom_bar(position="fill", stat="identity")+
  facet_wrap(facets = vars(temperature_c))+
  theme_bw()

```
3days graphed and grouped by avg close, avg open, avg semi but faceted by temperature
```{r}
duration_long_3days <- duration_long %>% 
  filter(duration== "3days")

ggplot(duration_long_3days, aes(x=genet,y=n, fill= status)) + 
  geom_bar(position="fill", stat="identity")+
  facet_wrap(facets = vars(temperature_c))+
  theme_bw()
```
3days graphed and grouped by avg close, avg open, avg semi but faceted by duration
```{r}
ggplot(grouped, aes(x=temperature_c,y=avg_open, fill=duration)) + 
  geom_bar(position="fill", stat="identity")+
 # facet_wrap(facets = vars(duration))+
  theme_bw()
```

Graphed with out genets and only the dat, temp duration + avg open, avg semi and avg close
```{r}
grouped <- recovery_observations_t %>% 
  mutate(not_open= (number_semi_open+ number_closed)) %>% 
  group_by(date, temp_c,duration) %>%
  summarize(avg_open = mean(number_open_complete),
          avg_close = mean(not_open)) %>% 
  mutate(duration= factor(duration,levels = c("24hr", "3days", "1week")))

ggplot(grouped, aes(x=temp_c, y= avg_open))+ 
  geom_boxplot()+
  facet_wrap(facets = vars(duration))+
  geom_jitter(color="black", size= 0.4, alpha= 7, width = 0.01)+
  labs(title = "Open c. Californica polyps per temperature & duration", x= "Temperature in C", y= "Average Open")+
  theme_bw()

ggsave(here("figures","Open c. Californica polyps per temperature & duration.png"),
       width= 10, height= 7)

group_24 <- grouped %>% 
  filter(duration=="24hr")
cory_anova <-aov(data=group_24,avg_open~temp_c) 
summary(cory_anova)
TukeyHSD(cory_anova)
```
observing the graphed with out genets and only the dat, temp duration + avg close
```{r}
ggplot(grouped, aes(x=temp_c, y= avg_close))+ 
  geom_boxplot()+
  facet_wrap(facets = vars(duration))+
  geom_jitter(color="black", size= 0.4, alpha= 7,width = 0.01)+
  labs(title = "Closed c. Californica polpys per temperature & duration", x= "Temperature in C", y= "Average Closed")+
  theme_bw()

ggsave(here("figures","Closed c. Californica polpys per temperature & duration.png"),
       width= 10, height= 7)
  
```

```{r}

group_24 <- grouped %>% 
  filter(duration=="24hr")

cory_anova <-aov(data=group_24,avg_close~temp_c) 
summary(cory_anova)
TukeyHSD(cory_anova)

```

imported death rates data set
```{r}
death_obs <- read_csv(here("data","death_obs.csv")) %>%
  clean_names() %>% 
  mutate(date= mdy(date))
```

I dont know what i was doing here
```{r}
death_obs_genet <- death_obs%>% 
  select(date, temperature_treatment_c, genet,original, current_n,duration) %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temperature_c= as.factor(temperature_treatment_c))
 
death_obs_genet_ex <- death_obs_genet[-649:-792 ,] %>% 
  group_by(date, genet,duration) %>% 
  summarize(original= mean(original),
            current_n= mean(current_n))
death_obs_genet_ex <- death_obs_genet[-649:-792 ,] %>% 
  group_by(date, genet,duration) %>% 
  summarise(original= sum(original),
            current_n= sum(current_n)) %>%
  filter(genet=="3", 
         duration == "1week")

death_1 <- death_obs %>%
  filter(genet=="3", 
         duration == "1week")

ggplot(death_obs_genet_ex, aes(x=date, y=current_n, color=genet))+
  geom_line()+
  facet_wrap(facets = vars(duration))

```



```{r}
recovery_merge <- recovery_observations %>% 
  filter(!is.na(number_open_complete)) %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp_c= as.factor(temperature_treatment)) %>% 
  mutate(date= mdy(date)) %>% 
  mutate(temp=gsub("°C","",temp_c)) %>% 
  select(date, time, temp, duration ,genet ,total_polyps , number_open_complete,
         number_semi_open, number_closed)
  
str(recovery_merge)
death_merge <- death_obs %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp= as.factor(temperature_treatment_c)) %>% 
  mutate(date= ymd(date)) %>% 
  select(date, time, temp, duration, genet, day, original, current_n )

death_recovery <- full_join(recovery_merge,death_merge) 

str(death_merge)
```

Generated the Death rate Figure
```{r}
death <- death_recovery %>% 
  mutate(day=as.factor(day)) %>% 
  group_by(day, genet,duration) %>% 
  summarise(original= sum(original),
            current_n= sum(current_n)) %>% 
   mutate(duration= factor(duration,levels = c("24hr", "3days", "1week")))
  

ggplot(death, aes(x=day, y=current_n, group=genet))+
  geom_line(aes(color=genet))+
  facet_wrap(facets = vars(duration))+
  scale_color_manual(values = c("1"="#FF5733","2"="#CD2E05","3"="#BA7F6D"))+
  labs(title = "Total c. Californica polpys vs death rates", x= "Day", y= "Total Polyps")+
  theme_bw()

ggsave(here("figures","Total c. Californica polpys vs death rates.png"),
       width= 10, height= 7)
```

Anova Test for each time duartion for all genets
```{r}
death_24 <- death %>% 
  filter(duration=="24hr")

cory_anova_24 <-aov(data=death_24,current_n~day) 
summary(cory_anova_24)
TukeyHSD(cory_anova_24)

death_3days <- death %>% 
  filter(duration=="3days")

cory_anova_3days <-aov(data=death_3days,current_n~day)
summary(cory_anova_3days)
TukeyHSD(cory_anova_3days)

death_week <- death %>% 
  filter(duration=="1week")

cory_anova_week <-aov(data=death_week,current_n~day)
summary(cory_anova_week)
TukeyHSD(cory_anova_week)
```

let me see if i can convert the death rate figure into a point and line
```{r}
ggplot(death, aes(x=day, y=current_n, group=genet))+
  geom_line(aes(color=genet))+
  facet_wrap(facets = vars(duration))+
  scale_color_manual(values = c("1"="#FF5733","2"="#CD2E05","3"="#BA7F6D"))+
  labs(title = "Total c. Californica polpys vs death rates", x= "Day", y= "Total Polyps")+
  theme_bw()
```



```{r}
test_run_bar <- recovery_observations %>% 
  select(date, temperature_treatment_c,duration, genet, number_open_complete,number_semi_open, number_closed) %>% 
  filter(!is.na(number_open_complete)) %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temperature_c= as.factor(temperature_treatment_c))

test_run_bar_2 <- test_run_bar %>% 
  group_by(date, temperature_c, duration, genet,avg_open) %>% 
  summarise(total= sum(number_open_complete, number_semi_open, number_closed))

  

```


str(death_recovery)

```{r}
# fission_3323 <- death_recovery %>%
#   filter(genet=="3",
#          duration == "3days",
#          temp == "23") %>%
#   arrange(date, time) %>%
#   #group_by(date, time) %>%
#   mutate(fission = total_polyps - lag(total_polyps, default=first(total_polyps)))
# 
# fission_3325 <- death_recovery %>%
#   filter(genet=="3",
#          duration == "3days",
#          temp == "25") %>%
#   arrange(date, time) %>%
#   #group_by(date, time) %>%
#   mutate(fission = total_polyps - lag(total_polyps, default=first(total_polyps)))
```






```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
