---
title: "reu_corynatcis_script"
output: html_document
date: '2022-10-17'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(hexbin)
library(patchwork)
library(RSQLite)
library(here)
library(janitor)
library(lubridate)

library(hrbrthemes)
library(viridis)
library(ggplot2)
library(reshape2)
```

created a data frame containg the excel csv sheet
```{r}
recovery_observations <- read_csv(here("data","Recovery_Observations.csv")) %>%
  clean_names()
```

Changed temperature column to a factor and removed all na values
```{r}
recovery_observations_t <- recovery_observations %>% 
  select(date, temperature_treatment,duration, genet, number_open_complete,number_semi_open, number_closed) %>% 
  filter(!is.na(number_open_complete)) %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp_c= as.factor(temperature_treatment))

```

Graphed with out genets and only the date, temp duration + avg open, avg semi and avg close
```{r}
grouped <- recovery_observations_t %>% 
  mutate(not_open= (number_semi_open + number_closed)) %>%
  group_by(date, temp_c,duration) %>%
  summarize(avg_open = mean((number_open_complete))/(number_open_complete+not_open),
          avg_close = mean((not_open))/(number_open_complete+not_open)) %>% 
  mutate(duration= factor(duration,levels = c("24hr", "3days", "1week")))
  

grouped_t <- groupe
  

ggplot(grouped, aes(x=temp_c, y= avg_open))+ 
  geom_boxplot()+
  facet_wrap(facets = vars(duration))+
  geom_jitter(color="black", size= 0.4, alpha= 7, width = 0.01)+
  labs(title = "Open polyps per temperature & duration", x= "Temperature in 째C", y= "Percentage Open")+
  #theme_bw()
  theme(text =(element_text(size=32)))

ggsave(here("figures","Open c. Californica polyps per temperature & duration.png"),
       width= 20, height= 7)
```

Checking the significant values for the number of polyps that wer opened
```{r}


group_24 <- grouped %>% 
  filter(duration=="24hr")
cory_anova <-aov(data=group_24,avg_open~temp_c) 
summary(cory_anova)
TukeyHSD(cory_anova)

group_3days <- grouped %>% 
  filter(duration=="3days")
cory_anova <-aov(data=group_3days,avg_open~temp_c)
summary(cory_anova)
TukeyHSD(cory_anova)

group_week <- grouped %>% 
  filter(duration=="1week")
cory_anova <-aov(data=group_week,avg_open~temp_c)
summary(cory_anova)
TukeyHSD(cory_anova)
```


observing the graphed with out genets and only the date, temp duration + avg close
```{r}

ggplot(group_week, aes(x=temp_c, y= avg_close))+ 
  geom_boxplot()+
  #facet_wrap(facets = vars(duration))+
  geom_jitter(color="black", size= 0.4, alpha= 7,width = 0.01)+
  labs(title = "Closed polpys per temperature for 1 week MHW ", x= "Temperature in 째C", y= "Percentage Closed")+
  #theme_bw()
  theme(text =(element_text(size=32)))+
  labs(title = str_wrap("Closed polpys per temperature for 1 week MHW ",40))

ggsave(here("figures","Closed polpys per temperature for 1 week MHW.png"),
       width= 12, height= 7)
  
```

```{r}

group_24_c <- grouped %>% 
  filter(duration=="24hr")

cory_anova <-aov(data=group_24_c,avg_close~temp_c) 
summary(cory_anova)
TukeyHSD(cory_anova)


group_3days_c <- grouped %>% 
  filter(duration=="3days")

cory_anova <-aov(data=group_3days_c,avg_close~temp_c) 
summary(cory_anova)
TukeyHSD(cory_anova)

group_week_c <- grouped %>% 
  filter(duration=="1week")

cory_anova <-aov(data=group_week_c,avg_close~temp_c) 
summary(cory_anova)
TukeyHSD(cory_anova)

```


new time series data for 24 hours during treatment
```{r}
twentyfour_death <- read_csv(here("data","24hrs_death.csv"))

twentyfour_death_f <- twentyfour_death %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp= as.factor(temp)) %>% 
  mutate(hours= as.factor(hours)) %>% 
  mutate(duration= as.factor(duration)) %>% 
  select(genet, temp, hours,current_polyps)

str(twentyfour_death_f)

ggplot(twentyfour_death_f, aes(x=hours, y=current_polyps, group=genet))+
  geom_line(aes(color=genet))+
  facet_wrap(facets = vars(temp))+
  scale_color_manual(values = c("1"="#FF5733","2"="#CD2E05","3"="#BA7F6D"))+
  labs(title = "Death rates in a 24 hour treatment", x= "Hours", y= "Current Polyps")+
  theme_bw()
ggsave(here("figures","Death rates in a 24 hour treatment.png"),
       width= 10, height= 7)
```

```{r}
three_death <- read_csv(here("data","3days_death.csv"))

three_death_f <- three_death %>% 
  select(genet, temp, hours,current_polyps) %>%  
  mutate(genet=as.character(genet)) %>% 
  mutate(temp= as.factor(temp)) %>% 
  mutate(hours= as.factor(hours)) 
  

str(three_death_f)

ggplot(three_death_f, aes(x=hours, y=current_polyps, group=genet))+
  geom_line(aes(color=genet))+
  facet_wrap(facets = vars(temp))+
  scale_color_manual(values = c("1"="#FF5733","2"="#CD2E05","3"="#BA7F6D"))+
  labs(title = "Death rates in a 3day treatment", x= "Hours", y= "Current Polyps")+
  theme_bw()

ggsave(here("figures","Death rates in a 3day treatment.png"),
       width= 10, height= 7)
```

```{r}
week_death <- read_csv(here("data","1week_death.csv"))

week_death_f <- week_death %>% 
  select(genet, temp, hours,current_polyps) %>%  
  mutate(genet=as.character(genet)) %>% 
  mutate(temp= as.factor(temp)) %>% 
  mutate(hours= as.factor(hours)) 
  

str(week_death_f)

ggplot(week_death_f, aes(x=hours, y=current_polyps, group=genet))+
  geom_line(aes(color=genet))+
  facet_wrap(facets = vars(temp))+
  scale_color_manual(values = c("1"="#FF5733","2"="#CD2E05","3"="#BA7F6D"))+
  labs(title = "Death rates in a 1 week treatment", x= "Hours", y= "Current Polyps")+
  theme_bw()
ggsave(here("figures","Death rates in a 1 week treatment.png"),
       width= 10, height= 7)
```
24 hour treatment but only the 27 temp treatment
```{r}
test_24 <- twentyfour_death_f %>% 
  filter(temp=="27")

ggplot(test_24, aes(x=hours, y=current_polyps, group=genet))+
  geom_line(aes(color=genet))+
  facet_wrap(facets = vars(temp))+
  scale_color_manual(values = c("1"="#F16A00","2"="#FF0C01","3"="#613508"))+
  labs(title = "Death rates in a 24 hour treatment", x= "Hours", y= "Current Polyps")+
  #theme_bw()
  theme(text =(element_text(size=24)))

ggsave(here("figures","Mortality rates in a 24 hour treatment.png"),
       width= 10, height= 7)
```
3day treatment but only the 27 temp treatment
```{r}
test_3days <- three_death_f %>% 
  filter(temp=="27")

ggplot(test_3days, aes(x=hours, y=current_polyps, group=genet))+
  geom_line(aes(color=genet))+
  facet_wrap(facets = vars(temp))+
  scale_color_manual(values = c("1"="#F16A00","2"="#FF0C01","3"="#613508"))+
  labs(title = "Death rates in a 3 day treatment", x= "Hours", y= "Current Polyps")+
  #theme_bw()
  theme(text =(element_text(size=24)))

ggsave(here("figures","Mortality rates in a 3 day treatment.png"),
       width= 10, height= 7)
```
week treatment but only the 27 temp treatment
```{r}
test_week <- week_death_f %>% 
  filter(temp=="27")

ggplot(test_week, aes(x=hours, y=current_polyps, group=genet))+
  geom_line(aes(color=genet))+
  facet_wrap(facets = vars(temp))+
  scale_color_manual(values = c("1"="#F16A00","2"="#FF0C01","3"="#613508"))+
  labs(title = "Death rates in a 1 week treatment", x= "Hours", y= "Current Polyps")+
  #theme_bw()
  theme(text =(element_text(size=24)))

ggsave(here("figures","Mortality rates in a 1 week treatment.png"),
       width= 10, height= 7)
```

significant trends
```{r}
week_death<- week_death_f %>% 
  filter(temp=="27")

week_ttest <-aov(data = week_death,current_polyps~hours) 
summary(week_ttest)
TukeyHSD(week_ttest)
```

```{r}
time_series_all <- read_csv(here("data","time_series_all.csv"))

time_series_27 <- time_series_all %>% 
  mutate(genet=as.character(genet)) %>% 
  mutate(temp= as.factor(temp)) %>% 
  mutate(hours= as.factor(hours)) %>% 
  mutate(duration= as.factor(duration)) %>% 
  mutate(duration= factor(duration,levels = c("24hrs", "3days", "1week"))) %>% 
  select(genet,duration, temp, hours,current_polyp) %>% 
  filter(temp=="27")
  
ggplot(time_series_27, aes(x=hours, y=current_polyp, group=genet))+
  geom_line(aes(color=genet, size= 0.1))+
  facet_wrap(facets = vars(duration))+
  scale_color_manual(values = c("1"="#F16A00","2"="#FF0C01","3"="#613508"))+
  labs(title = "Mortality rates in a 27째C treatment per duration", x= "Hours", y= "Current Polyps")+
  theme(text=(element_text(size=32)))
  
ggsave(here("figures", "Mortality rates in a 27째C treatment per duration.png"),
       width= 20, height= 7)
```

