---
title: "Untitled"
output: html_document
date: '2022-07-27'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(hexbin)
library(patchwork)
library(RSQLite)
library(here)
library(janitor)
library(lubridate)
```

install packages
```{r}
library(tidyverse)
library(hexbin)
library(patchwork)
library(RSQLite)
library(here)
library(janitor)
library(lubridate)
```

thats where i installed my packages

example on doing data collection
```{r pressure, echo=FALSE, messages=FALSE}
t1_tank <- read_csv(here("data","0715_T1.csv")) %>% 
  clean_names() %>% 
  mutate(tank_number="Tank 1",date_time= mdy_hm(date))
str(t1_tank)
```

get tank 1 together
```{r}
t1_tank_1 <- read_csv(here("data","0726-0727_T1_0.csv")) %>% 
  clean_names() %>%  
  mutate(tank_number="Tank 1",date= mdy_hm(date)) %>% 
  select(date, temp_c, tank_number)
  





t1_tank_2 <- read_csv(here("data","Experiement_0803_T1_0.csv")) %>% 
  clean_names() %>%  
  mutate(tank_number="Tank 1",date= mdy_hm(date)) %>% 
  select(date, temp_c, tank_number)

t1_tank <- full_join(t1_tank_1,t1_tank_2)




```

tank 2
```{r}
t2_tank_1 <- read_csv(here("data","0726-0727_T2.csv")) %>% 
  clean_names() %>%  
  mutate(tank_number="Tank 2",date= mdy_hm(date)) %>% 
  select(date, temp_c, tank_number)

t2_tank_2 <- read_csv(here("data","Experiment_0803_T2.csv")) %>% 
  clean_names() %>%  
  mutate(tank_number="Tank 2",date= mdy_hm(date)) %>% 
  select(date, temp_c, tank_number)

t2_tank <- full_join(t2_tank_1,t2_tank_2)

```
tank 3
```{r}
t3_tank_1 <- read_csv(here("data","0726-0727_T3.csv")) %>% 
  clean_names() %>%  
  mutate(tank_number="Tank 3 ",date= mdy_hm(date)) %>% 
  select(date, temp_c, tank_number)

t3_tank_2 <- read_csv(here("data","Experiment_0803_T3.csv")) %>% 
  clean_names() %>%  
  mutate(tank_number="Tank 3",date= mdy_hm(date)) %>% 
  select(date, temp_c, tank_number)

t3_tank <- full_join(t3_tank_1,t3_tank_2)
```
ambient
```{r}
ambient <- read_csv(here("data","Experiment_0803_Amb.csv")) %>% 
  clean_names() %>%  
  mutate(tank_number="Tank 0",date= mdy_hm(date)) %>% 
  select(date, temp_c, tank_number)
```

merge all temperatures together
```{r}
sump_1 <- full_join(t1_tank, t2_tank)
sump_2 <- full_join(t3_tank, ambient)

sump_tank <- full_join(sump_1 ,sump_2) %>% 
  select(date, temp_c, tank_number) %>% 
  filter(!is.na(temp_c)) %>% 
  filter(date<=ymd_hms("2022-07-27 9:30:00")|date>= ymd_hms("2022-07-27 10:30:00")) %>% 
  filter(date>ymd_hms("2022-07-26 11:30:00")) %>% 
  filter(date<ymd_hms("2022-08-03 8:00:00")) %>% 
  filter(date>ymd_hms("2022-07-28 00:00:00"))

sump_tank_sum <- sump_tank %>% 
  filter(date>ymd_hms("2022-07-28 00:00:00")) %>% 
  group_by( tank_number) %>% 
  summarize(mean= mean(temp_c), min=min(temp_c), max= max(temp_c), sd= sd(temp_c))

head(sump_tank)
str(sump_tank)
```
lets plot them all together
```{r}
ggplot(data= sump_tank, mapping= aes(x=date, y=temp_c, group= tank_number))+
  geom_line(aes(color= tank_number))+
  labs(title = "Temperature Treamtent", x= "Date", y= "Temperature in C")

ggsave(here("figures","Temperature Treamtent.png"),
       width= 10, height= 7)
  
  
```

created a new data frame with just dates and temp while also 
filtering out the na values in the temp_c cloumn
```{r}
t1_temp_graph <- t1_tank %>%
  select(date_time, temp_c) %>% 
  filter(!is.na(temp_c))
  
```




plotted the t1_temp_graph
```{r}
ggplot(t1_temp_graph, aes(x= date_time, y=temp_c))+
  geom_point(size=0.1)
```

view data
```{r}
view(t1_temp_graph)
```


excluded unnecessary values
```{r}
t1_temp_graph[c(-1:-30, -680:-885),]
```
new code exluding the values before row 10
```{r}
t1_temp_graph_ex <- t1_temp_graph[c(-1:-30, -680:-885),]


view(t1_temp_graph_ex)

```

```{r}

```


plotting new graph 
```{r}
ggplot(t1_temp_graph_ex, aes(x=date_time,y=temp_c)) +
  geom_point(size=0.01)+
  geom_line(aes(group=1))

sum(1,2,3)
```
```{r}
ggplot(t1_temp_graph_ex, aes(x=date_time,y=temp_c))+
  geom_line(aes(group=1), size=0.75)
```

plotting new graph with differnt x and y values
```{r}

  ggplot(t1_temp_graph_ex, aes(x=date_time,y=temp_c))+
  geom_line(group=1, size=0.75)+
  labs(title = "Tank 1 Temp", x= "Date", y= "temperature in C")+
  scale_y_continuous(limits=c(15,30))+
  theme_bw()

ggsave(here("figures","Tank 1 Temp.png"), width= 10, height= 7)
```

imported the complete temperature logs from 07/26/22-08/03/22 and exclued the times where
```{r}
t1_tank <- read_csv(here("data","0726-0727_T1_0.csv")) %>% 
  clean_names() %>% 
  mutate(date= mdy_hm(date)) %>% 
  select(date, temp_c) %>% 
  filter(!is.na(temp_c))

t1_tank_ex <- t1_tank %>% 
  filter(date>="2022-07-26 11:28:00") %>% 
  filter(!(temp_c==24.738)) %>% 
  filter(!(temp_c==27.567)) %>% 
  filter(!(temp_c==26.977)) %>% 
  filter(!(temp_c==25.42970)) %>% 
  filter(!(temp_c==25.42819)) %>% 
  filter(!(temp_c==25.43121))
  

  filter(!(temp_c==25.43121)) %>%
  filter(!(temp_c==25.42970)) %>% 
  filter(!(temp_c==26.97700)) %>% 
  filter(!(temp_c==25.42819)) %>% 
  filter(!(temp_c==25.42970)) %>% 
  filter(!(temp_c==25.42819)) %>% 
  filter(!(temp_c==25.43121))
  
 
  
  


ggplot(t1_tank_ex, aes(x=date,y=temp_c))+
  geom_line(group=1, size=0.75)+
  labs(title = "Tank 1 Temp", x= "Date", y= "temperature in C")+
  scale_y_continuous(limits=c(15,30))+
  theme_bw()
ggplot(t1_tank_ex, aes(x=date,y=temp_c))+
  geom_point()


```

filter dates that i dont need
```{r}

```


```{r}
sample.int(6,3)
```

